---
title: "Data Tidying and Reporting – Task 1"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: false
    number_sections: false
    highlight: tango
    latex_engine: xelatex
    fig_caption: true
    extra_dependencies:
      - geometry
bibliography: references.bib
nocite: '@*'
link-citations: yes
linkcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.bg = "transparent")
```

```{r load_libraries, include=FALSE}
library(glmnet)
library(ggplot2)

#' Installation of required packages
#' Before running this file, make sure you have the following packages installed:
#' - glmnet
#' - ggplot2
#' You can install these packages using the install.packages() function in R:
#' install.packages(c("glmnet", "ggplot2"))
```


## Introduction

Handwritten digit recognition involves the conversion of human handwritten digit images into digital representations. This task might be challenging due to humans imperfections and the wide variability of handwritten forms. As well as some digits might look similar, increasing the difficulty of the task.

The dataset used for this project has been provided by the professor in the file named `qmnist_nist.RData`. It contains both the training and testing datasets, storing the images as a collections of pixel values. This report focuses on using ridge logistic regression to distinguish between handwritten digits, specifically $4$ and $9$, and lately this procedure has been extrapolated to the classification problems of one versus another digit.

## Methodology

Ridge logistic regression is a regularization technique used for classification tasks, which involves adding a penalty term, $\lambda\sum_{j=1}^n \beta_j^2$, to the loss function. This term reduces model complexity and helps prevent overfitting. This technique is suited for high-dimensional data like images. Below, we detail the methodology applied in this project:

1.  **Data preprocessing**. The initial step involves preparing both, training and testing sets. The data is filtered to include only the images representing the two digits of interest. Then it is formatted properly to ensure compatibility with the computational model.

2.  **Model training**. In this phase, we search for the optimal $\lambda$ value which helps in making a good model (not too simple, not too complex). It is worth to mention that we do not standardize the predictors; this decision is based on the consistent scale and range of pixel values across the handwritten digit images.

3.  **Model evaluation**. The performance of our trained model is assessed using a reserved test set. The evaluation metric is the accuracy, defined as the proportion of the number of correctly identified digits to the total number of digits in the test set.

4. **Model visualization**. Through two plots, we are able to understand the model's strategy in distinguishing between digits. The *Estimated $\beta$ coefficient* shows the magnitude and direction of this parameter ($\beta$) over the pixel index ($28$x$28$=$784$ points). The higher the magnitude values, the greater their contribution is. Meanwhile, the *Average rank of $\beta$ coefficients* uses a gradient from white (no relevant) to blue (high relevant) to highlights the importance of each pixel for the model's decision, shown on a $28$x$28$ grid.

```{r utility_functions, echo=FALSE}
# Functions --------------------------------------------------------------------

#' Prepare data for glmnet model
#'
#' Filters a dataset for two specified digits and formats it for use with glmnet,
#' transforming pixel values to a matrix format and digit labels to a binary outcome.
#'
#' @param data Dataset containing the digit images and labels.
#' @param digits Vector of two elements indicating the digits to filter.
#' @return A list with matrix 'x' of pixel values and vector 'y' of binary outcomes.
prepare_data <- function(data, digits) {
  ind <- data$digit %in% digits
  x <- as.matrix(data$px[ind, ])
  y <- ifelse(data$digit[ind] == as.numeric(digits[1]), 1, 0)
  list(x = x, y = y)
}

#' Train and evaluate a model, and compute beta coefficients
#'
#' This function trains a logistic regression model using ridge regularization to classify
#' between two specific digits. It performs cross-validation to find the optimal
#' regularization parameter (lambda), fits the model with this optimal lambda, predicts on
#' a test dataset, evaluates accuracy, and extracts beta coefficients for the model.
#'
#' @param digit_a The first digit to classify.
#' @param digit_b The second digit to classify.
#' @param train_data Training dataset used for model fitting.
#' @param test_data Test dataset used for model evaluation.
#' @return A list containing the model's accuracy, optimal lambda, and beta values.
train_and_evaluate <- function(digit_a, digit_b, train_data, test_data) {
  data_train <- prepare_data(train_data, c(digit_a, digit_b))
  data_test <- prepare_data(test_data, c(digit_a, digit_b))

  # Perform cross-validation to find the optimal lambda
  cv_model <- cv.glmnet(
    x = data_train$x,
    y = data_train$y,
    alpha = 0,
    family = "binomial",
    nfolds = 10,
    standardize = FALSE
  )

  lambda_optimal <- cv_model$lambda.min

  # Fit the model with the optimal lambda
  model <- glmnet(
    x = data_train$x,
    y = data_train$y,
    alpha = 0,
    lambda = lambda_optimal,
    family = "binomial",
    standardize = FALSE
  )

  # Predict on the test data and evaluate its accuracy
  predictions <- predict(model, newx = data_test$x, s = lambda_optimal, type = "response")
  accuracy <- mean((predictions > 0.5) == data_test$y)

  # Extract beta coefficients, excluding the intercept
  beta_values <- as.vector(coef(model, s = lambda_optimal)[-1])

  list(accuracy = accuracy, lambda = lambda_optimal, beta_values = beta_values)
}

#' Plot beta coefficients
#'
#' Show the magnitude and direction of the beta coefficients over the pixel index,
#' 784 pixels.
#'
#' @param lambda_optimal The optimal lambda value for regularization chosen by
#' cross-validation.
#' @param digit_a The first digit to classify.
#' @param digit_b The second digit to classify.
#' @param train_data Training dataset used to fit the model.
plot_beta_coef <- function(lambda_optimal, digit_a, digit_b, train_data) {
  data_train <- prepare_data(train_data, c(digit_a, digit_b))
  # Fit the model with the optimal lambda
  model <- glmnet(
    x = data_train$x,
    y = data_train$y,
    alpha = 0,
    lambda = lambda_optimal,
    family = "binomial",
    standardize = FALSE
  )

  # Extract beta coefficients, excluding the intercept
  beta_values <- as.vector(coef(model, s = lambda_optimal)[-1])
  df_beta <- data.frame(PixelIndex = 1:length(beta_values), BetaValue = beta_values)

  # Create the plot
  ggplot(df_beta, aes(x = PixelIndex, y = BetaValue)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5)) +
    labs(
      title = expression(paste("Estimated ", beta, " coefficients")),
      x = "Pixel index",
      y = expression(paste(beta, " value"))
    )
}

#' Visualize average rank of beta coefficients
#'
#' Creates a heatmap visualization of the average rank of beta coefficients on a 28x28 grid.
#' The gradient from white (less relevant) to blue (more relevant) highlights the importance
#' of each pixel for the model's decision.
#'
#' @param beta_ranks A vector of beta coefficient ranks.
visualize_beta_ranks <- function(beta_ranks) {
  # Reshape into a 28x28 matrix for visualization
  beta_rank_matrix <- matrix(beta_ranks, nrow = 28, byrow = TRUE)
  # Matrix into data frame for using ggplot2
  beta_rank_df <- expand.grid(
    Var1 = 1:nrow(beta_rank_matrix),
    Var2 = 1:ncol(beta_rank_matrix)
  )
  beta_rank_df$value <- as.vector(beta_rank_matrix)

  # Create the plot
  ggplot(beta_rank_df, aes(x = Var1, y = Var2, fill = value)) +
    geom_tile() +
    scale_fill_gradient(low = "white", high = "blue", name = "Rank") +
    labs(
      title = expression(paste("Average rank of ", beta, " coefficients")),
      x = "Pixel column",
      y = "Pixel row"
    ) +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5))
}

#' Display an image of a digit
#'
#' Display an image of a digit based on provided pixel values. The default color scheme
#' is scale of gray.
#'
#' @param x Vector of pixel values representing the digit image.
#' @param col Color scheme for the image, defaults to gray scale.
show_digit <- function(x, col = gray(255:1 / 255), ...) {
  l <- sqrt(length(x))
  image(matrix(as.numeric(x), nrow = l)[, l:1], col = col, ...)
}
```


```{r prepare_enviroment, echo=FALSE}
# Prepare the environment ------------------------------------------------------
set.seed(42) # Ensures reproducibility
load(file = "qmnist_nist.RData")
```


## Results

```{r classification_AvsB, eval=FALSE, include=FALSE}
# Example of classification task digit_a vs digit_b ----------------------------
digit_a <- 4
digit_b <- 9

result_ab <- train_and_evaluate(digit_a, digit_b, train_nist, test_nist)
sprintf("Accuracy for %d vs %d: %f", digit_a, digit_b, result_ab$accuracy)
sprintf("Optimal lambda for %d vs %d: %f", digit_a, digit_b, result_ab$lambda)

plot_beta_coef(result_ab$lambda, digit_a, digit_b, train_nist)

# Heatmap for beta coefficient
beta_absolute <- abs(result_ab$beta_values)
beta_ranks <- rank(beta_absolute, ties.method = "average")
visualize_beta_ranks(beta_ranks)
```


```{r classification_4vs9, echo=FALSE}
# Classification task 4 vs 9 ---------------------------------------------------
digit_a <- 4
digit_b <- 9

# Results are precomputed
beta_ranks_49 <- c(
  93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93,
  93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93,
  93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 93, 198, 206, 195, 93, 220, 217, 199, 202, 93, 93, 93, 93, 93,
  93, 93, 93, 93, 93, 93, 93, 93, 93, 223, 239, 234, 210, 263, 290, 273, 288, 311, 607, 343, 257, 245, 225, 226, 205, 188, 93, 93,
  93, 93, 93, 93, 203, 232, 219, 214, 227, 244, 241, 259, 385, 389, 475, 615, 516, 414, 536, 433, 408, 363, 298, 323, 342, 297, 209, 93,
  93, 93, 93, 197, 213, 246, 340, 377, 459, 467, 533, 411, 320, 636, 393, 537, 687, 269, 416, 367, 526, 464, 657, 670, 489, 303, 200, 93,
  93, 93, 93, 208, 264, 518, 394, 296, 554, 506, 362, 652, 488, 560, 741, 760, 773, 751, 749, 585, 697, 432, 753, 679, 601, 339, 287, 93,
  93, 93, 93, 251, 372, 674, 565, 482, 317, 293, 703, 710, 783, 775, 748, 762, 782, 655, 779, 664, 722, 678, 480, 633, 735, 512, 248, 93,
  93, 93, 186, 305, 479, 619, 558, 662, 476, 330, 235, 593, 568, 777, 778, 727, 772, 765, 704, 548, 446, 676, 648, 421, 604, 528, 252, 93,
  93, 93, 192, 299, 469, 383, 502, 577, 352, 504, 551, 626, 594, 677, 781, 780, 730, 574, 327, 306, 427, 572, 483, 539, 608, 417, 250, 93,
  93, 93, 215, 265, 466, 388, 387, 578, 503, 445, 540, 557, 473, 595, 776, 599, 353, 646, 668, 542, 374, 620, 628, 754, 696, 470, 258, 93,
  93, 93, 406, 236, 364, 494, 587, 369, 685, 275, 653, 266, 752, 228, 699, 747, 728, 396, 645, 622, 732, 637, 365, 666, 658, 294, 284, 93,
  93, 93, 307, 381, 550, 606, 714, 334, 249, 511, 556, 723, 784, 758, 660, 610, 328, 583, 625, 688, 632, 580, 592, 439, 643, 514, 310, 93,
  93, 93, 204, 458, 659, 441, 376, 301, 546, 611, 667, 736, 757, 371, 669, 322, 675, 423, 448, 501, 336, 438, 555, 271, 449, 472, 368, 93,
  93, 93, 93, 434, 435, 500, 498, 712, 477, 661, 617, 651, 521, 513, 584, 614, 549, 280, 590, 618, 451, 510, 603, 302, 462, 337, 211, 93,
  93, 93, 93, 419, 315, 373, 561, 425, 724, 742, 316, 698, 654, 324, 707, 553, 319, 544, 672, 683, 329, 605, 532, 515, 390, 270, 253, 189,
  93, 93, 255, 621, 631, 428, 391, 746, 689, 497, 378, 496, 455, 527, 743, 726, 405, 509, 478, 684, 768, 766, 671, 616, 332, 237, 194, 191,
  93, 93, 520, 630, 729, 579, 624, 531, 447, 640, 638, 256, 582, 650, 734, 508, 711, 291, 279, 602, 733, 686, 718, 596, 355, 230, 207, 190,
  247, 93, 430, 647, 600, 566, 681, 348, 292, 313, 642, 538, 767, 700, 682, 612, 725, 384, 468, 644, 522, 341, 535, 491, 358, 426, 229, 187,
  93, 93, 285, 552, 529, 530, 486, 402, 499, 410, 338, 719, 346, 691, 701, 755, 673, 333, 490, 721, 564, 569, 463, 314, 351, 453, 222, 93,
  93, 93, 268, 318, 395, 507, 281, 350, 403, 440, 589, 627, 665, 409, 276, 375, 694, 484, 272, 397, 461, 420, 424, 304, 380, 429, 93, 93,
  93, 93, 212, 242, 485, 543, 444, 361, 656, 262, 635, 581, 492, 570, 717, 243, 641, 471, 588, 412, 399, 382, 349, 415, 360, 240, 93, 93,
  93, 93, 93, 238, 366, 386, 431, 325, 505, 623, 456, 401, 286, 442, 586, 609, 457, 639, 454, 597, 370, 326, 524, 460, 331, 277, 261, 93,
  93, 93, 93, 233, 308, 517, 613, 740, 562, 437, 545, 519, 407, 523, 738, 534, 690, 474, 404, 649, 573, 379, 278, 295, 231, 283, 260, 93,
  93, 93, 93, 93, 547, 567, 708, 705, 680, 398, 737, 634, 571, 576, 493, 713, 598, 392, 443, 274, 254, 218, 312, 309, 201, 282, 93, 93,
  93, 93, 193, 93, 345, 300, 663, 715, 764, 744, 422, 692, 739, 591, 695, 771, 693, 716, 756, 731, 495, 418, 450, 356, 216, 224, 93, 93,
  93, 93, 93, 221, 413, 487, 289, 706, 745, 759, 770, 750, 763, 761, 769, 774, 720, 629, 709, 702, 525, 436, 452, 335, 196, 93, 93, 93,
  93, 93, 93, 93, 93, 93, 354, 575, 559, 357, 563, 541, 481, 347, 344, 267, 321, 359, 465, 400, 93, 93, 93, 93, 93, 93, 93, 93
)
result_49 <- list(percentage = 97.799, lambda = 21.9758474587424)
```


**$\text{\underline{4 vs 9 classifier}}$**. The model classifier showcased a remarkable ability to differentiate between digits $4$ and $9$, achieving an accuracy of `r result_49$percentage`%. Two critical regions are identified over the blue areas. The left region, in particular, captures the curve of the digit $9$, contrasting with the peak characteristic of the digit $4$. 

```{r classification_4vs9_plot, echo=FALSE, out.width="40%"}
plot_beta_coef(result_49$lambda, digit_a, digit_b, train_nist)
visualize_beta_ranks(beta_ranks_49)
```


```{r classification_all_digits, eval=FALSE, include=FALSE}
# Optional analysis - Comparing all digit pairs ------------------------------------
digits <- 0:9
# Initialize structures to store results
lambda_optimals <- matrix(0, nrow = 10, ncol = 10, dimnames = list(digits, digits))
accuracy_matrix <- matrix(0, nrow = 10, ncol = 10, dimnames = list(digits, digits))
beta_aggregate <- numeric(784) # For 28x28 images

# Iterate over all unique pairs of digits -> This execution takes a while
for (i in digits) {
  for (j in digits) {
    # To ensure each pair is only evaluated once
    if (j > i) {
      result <- train_and_evaluate(i, j, train_nist, test_nist)
      accuracy_matrix[i + 1, j + 1] <- result$accuracy
      lambda_optimals[i + 1, j + 1] <- result$lambda
      # Using absolute values for simplicity
      beta_aggregate <- beta_aggregate + abs(result$beta_values)

      print(paste(i, "vs", j)) # Progress feedback
    }
  }
}

# Average beta values
beta_aggregate <- beta_aggregate / (length(digits) * (length(digits) - 1) / 2)
beta_ranks <- rank(beta_aggregate, ties.method = "average")
visualize_beta_ranks(beta_ranks)

print(lambda_optimals)
print(accuracy_matrix)

# Compute some overall insight
average_accuracy <- sum(accuracy_matrix[accuracy_matrix > 0]) / 45 # 45 models are evaluated
highest_accuracy <- max(accuracy_matrix[accuracy_matrix > 0])
# Index start at 1, digits goes 0-9
highest_position <- which(accuracy_matrix == highest_accuracy, arr.ind = TRUE) - 1
lowest_accuracy <- min(accuracy_matrix[accuracy_matrix > 0])
lowest_position <- which(accuracy_matrix == lowest_accuracy, arr.ind = TRUE) - 1
```


```{r precomputed_lambda, eval=FALSE, include=FALSE}
# Precomputed data: lambda
lambda_precomputed <- c(
  0, 11.72903, 39.492636, 24.853003, 10.164498, 16.669416, 7.167558, 4.786700, 29.91104, 16.311870,
  0, 0, 4.386601, 9.245058, 10.907331, 4.542014, 7.198158, 5.834560, 24.04870, 5.250782,
  0, 0, 0, 49.861094, 33.663612, 15.672550, 10.926998, 19.236063, 34.30107, 5.962494,
  0, 0, 0, 0, 4.527115, 39.707292, 4.517932, 20.517036, 52.98839, 13.550726,
  0, 0, 0, 0, 0, 9.765175, 15.969006, 12.924441, 24.75766, 20.023574,
  0, 0, 0, 0, 0, 0, 21.776718, 4.110943, 59.91032, 23.640739,
  0, 0, 0, 0, 0, 0, 0, 10.752439, 11.15123, 8.774185,
  0, 0, 0, 0, 0, 0, 0, 0, 10.33513, 35.950445,
  0, 0, 0, 0, 0, 0, 0, 0, 0, 21.651250,
  0, 0, 0, 0, 0, 0, 0, 0, 0, 0
)

# Load precomputed: lambda optimal
lambda_data <- matrix(lambda_precomputed, nrow = 10, ncol = 10, byrow = TRUE)
rownames(lambda_data) <- colnames(lambda_data) <- as.character(0:9) # Assign row and column names
print(lambda_data)
```


```{r precomputed_accuracy, include=FALSE}
# Precomputed data: accuracy
accuracy_precomputed <- c(
  0, 0.9996938, 0.9925422, 0.9940961, 0.9971919, 0.9896266, 0.9931395, 0.9974579, 0.9936233, 0.9965301,
  0, 0, 0.9979857, 0.9972532, 0.9987382, 0.9968699, 0.9992197, 0.9974164, 0.9900031, 0.9977911,
  0, 0, 0, 0.9786718, 0.9897925, 0.9872064, 0.9900728, 0.9930824, 0.9816164, 0.9889521,
  0, 0, 0, 0, 0.9970370, 0.9745047, 0.9980466, 0.9925574, 0.9718103, 0.9911082,
  0, 0, 0, 0, 0, 0.9935622, 0.9947723, 0.9941003, 0.9935854, 0.9773038,
  0, 0, 0, 0, 0, 0, 0.9895760, 0.9967421, 0.9759462, 0.9923077,
  0, 0, 0, 0, 0, 0, 0, 0.9996759, 0.9939920, 0.9979757,
  0, 0, 0, 0, 0, 0, 0, 0, 0.9943219, 0.9801639,
  0, 0, 0, 0, 0, 0, 0, 0, 0, 0.9890240,
  0, 0, 0, 0, 0, 0, 0, 0, 0, 0
)

# Load precomputed: accuracy matrix
accuracy_precomputed <- matrix(accuracy_precomputed, nrow = 10, ncol = 10, byrow = TRUE)
rownames(accuracy_precomputed) <- colnames(accuracy_precomputed) <- as.character(0:9)
print(accuracy_precomputed)

# Compute some overall insight
average_accuracy <- sum(accuracy_precomputed[accuracy_precomputed > 0]) / 45
percentage_average <- round(average_accuracy * 100, digits = 3)
highest_accuracy <- max(accuracy_precomputed[accuracy_precomputed > 0])
percentage_best <- round(highest_accuracy * 100, digits = 3)
highest_position <- which(accuracy_precomputed == highest_accuracy, arr.ind = TRUE) - 1
lowest_accuracy <- min(accuracy_precomputed[accuracy_precomputed > 0])
percentage_lowest <- round(lowest_accuracy * 100, digits = 3)
lowest_position <- which(accuracy_precomputed == lowest_accuracy, arr.ind = TRUE) - 1
```


**$\text{\underline{General classifier}}$**. Classify one digit versus another involves the creation of $45$ different models. This approach yielded an incredible average accuracy of `r percentage_average`%. Among these, the best performing was between digits `r highest_position[1]` and `r highest_position[2]`, achieving an accuracy of `r percentage_best`%. On the other hand, even the worst model gets a `r percentage_lowest`% of accuracy which was obtained by digits `r lowest_position[1]` and `r lowest_position[2]`.

The visualization of pixel importance across all classifications showcases a pattern: pixels within blue regions are most located in the central area of the images, indicating their crucial role in the definition of the shape of the digits. Conversely, areas in white which hold less importance, are typically found at the edges and corners of the images.

```{r precomputed_beta_ranks, echo=FALSE, out.width="40%", fig.align = 'center'}
# Precomputed data: beta ranks average for the 45 classification task
beta_ranks_precomputed <- c(
  37, 37, 37, 37, 37, 37, 37, 37, 37, 37, 37, 37, 37, 37, 37, 37, 37, 37, 37, 37, 120, 200, 205, 126, 37, 37, 37, 37,
  37, 37, 37, 37, 81, 86, 124, 141, 154, 161, 186, 166, 196, 176, 169, 228, 258, 233, 173, 209, 194, 162, 220, 181, 37, 37, 37,
  37, 37, 37, 75, 96, 122, 102, 133, 177, 207, 234, 262, 273, 259, 264, 266, 285, 302, 284, 294, 281, 236, 248, 230, 183, 164, 149, 37,
  37, 37, 37, 103, 109, 137, 202, 212, 245, 275, 272, 296, 324, 362, 393, 417, 480, 451, 425, 462, 414, 392, 354, 311, 265, 211, 167, 37,
  37, 37, 74, 127, 106, 123, 246, 263, 307, 310, 320, 358, 377, 477, 623, 589, 551, 590, 540, 531, 407, 386, 437, 438, 421, 368, 283, 178,
  112, 37, 37, 108, 143, 163, 295, 309, 342, 347, 380, 435, 450, 527, 735, 646, 510, 713, 541, 441, 626, 543, 548, 549, 615, 428, 298, 170,
  37, 37, 95, 182, 219, 247, 314, 335, 371, 434, 479, 431, 422, 454, 501, 561, 635, 688, 568, 486, 493, 560, 426, 572, 586, 553, 340, 226,
  119, 37, 160, 223, 239, 329, 388, 382, 398, 463, 498, 460, 564, 640, 606, 538, 668, 751, 705, 614, 478, 418, 499, 559, 537, 542, 375, 241,
  114, 147, 156, 222, 244, 339, 445, 378, 411, 471, 455, 489, 508, 519, 518, 528, 515, 691, 682, 706, 660, 627, 556, 702, 739, 725, 427, 253,
  129, 117, 180, 213, 271, 350, 390, 403, 402, 529, 512, 476, 583, 554, 484, 631, 598, 557, 701, 722, 711, 569, 653, 730, 771, 741, 448, 256,
  158, 121, 168, 238, 289, 361, 356, 372, 466, 573, 509, 685, 671, 535, 503, 715, 736, 717, 729, 732, 699, 641, 642, 714, 767, 745, 384, 267,
  152, 97, 172, 237, 291, 370, 334, 424, 456, 684, 704, 723, 658, 689, 639, 726, 708, 747, 678, 695, 555, 731, 672, 657, 674, 648, 367, 261,
  148, 37, 130, 232, 282, 364, 363, 458, 497, 621, 697, 690, 765, 753, 770, 759, 775, 780, 680, 628, 743, 571, 655, 603, 577, 399, 321, 277,
  142, 87, 146, 206, 270, 366, 389, 387, 649, 634, 757, 777, 693, 773, 779, 769, 772, 774, 716, 632, 677, 565, 727, 681, 679, 433, 344, 287,
  204, 125, 138, 184, 260, 338, 376, 511, 656, 613, 675, 719, 746, 748, 768, 776, 778, 766, 724, 579, 444, 459, 526, 496, 624, 430, 348, 250,
  115, 105, 37, 155, 280, 360, 394, 491, 585, 694, 738, 633, 718, 764, 783, 784, 707, 692, 710, 546, 483, 629, 470, 396, 495, 406, 345, 257,
  83, 98, 93, 216, 319, 369, 381, 600, 734, 683, 698, 733, 762, 760, 781, 763, 625, 654, 687, 488, 517, 604, 481, 404, 429, 401, 328, 251,
  118, 37, 92, 249, 331, 409, 419, 578, 580, 669, 744, 754, 756, 758, 782, 703, 662, 686, 594, 467, 664, 574, 534, 523, 443, 436, 326, 221,
  179, 128, 91, 214, 353, 473, 544, 651, 596, 740, 750, 712, 666, 721, 638, 584, 570, 636, 452, 532, 619, 487, 494, 506, 423, 385, 317, 197,
  144, 79, 135, 217, 333, 464, 601, 644, 737, 742, 700, 728, 665, 643, 536, 607, 550, 645, 592, 416, 552, 442, 447, 593, 439, 341, 304, 192,
  100, 37, 132, 215, 323, 533, 608, 720, 755, 752, 749, 761, 622, 562, 520, 652, 521, 612, 558, 513, 514, 469, 415, 432, 336, 312, 274, 174,
  84, 89, 101, 210, 288, 400, 605, 696, 602, 566, 647, 659, 673, 610, 591, 547, 567, 595, 524, 516, 492, 472, 405, 374, 305, 292, 231, 195,
  76, 88, 82, 189, 268, 355, 502, 676, 611, 465, 597, 449, 617, 663, 563, 525, 490, 530, 670, 461, 474, 420, 359, 327, 290, 254, 235, 131,
  78, 37, 37, 165, 252, 349, 391, 482, 468, 475, 545, 599, 709, 539, 576, 667, 616, 620, 587, 413, 379, 365, 315, 308, 276, 240, 227, 139,
  37, 37, 37, 151, 225, 313, 408, 582, 650, 581, 500, 637, 609, 618, 661, 485, 457, 453, 440, 383, 351, 297, 278, 269, 242, 224, 198, 110,
  37, 37, 37, 116, 140, 286, 357, 397, 505, 630, 588, 575, 522, 504, 395, 412, 507, 446, 410, 373, 346, 300, 255, 243, 199, 136, 113, 107,
  37, 37, 37, 37, 111, 229, 301, 322, 299, 306, 332, 352, 316, 325, 330, 343, 337, 318, 293, 303, 279, 218, 188, 157, 145, 90, 77, 37,
  37, 37, 37, 37, 37, 80, 94, 134, 185, 187, 153, 203, 190, 201, 191, 193, 159, 171, 175, 208, 150, 104, 99, 85, 37, 37, 37, 37, 37
)

# Heatmap for visualization beta rank coefficients
visualize_beta_ranks(beta_ranks_precomputed)
```


## Conclusion

The ridge logistic model has demonstrated an outstanding performance across all tasks, distinguishing greatly between pairs of digits. Therefore, it can be concluded that the chosen model is a great selection for this classification problem. Lastly, it is important to mention that this report focuses on presenting key insights and a comprehensive explanation. For those interested in the implementation details, the full code is available in the R Markdown script.


## References

<div id="refs"></div>
